### 2015-11-06 CVPR16/Source/experiments2.tex

\subsection{Localization Experiment and Results}
We report error in three metrics translation error (t) in meters per car, yaw
error (yaw) in radians per car and dimension error is again meters per car. The
results are shown in Table~\ref{tab:localizationExperiment}.  We compare four
combinations of energies as shown in the table.  The energy $\EnergyTrackNoOcc$
represents the point tracks energy modeled with accounting for occlusion, i.e.,
we remove the term $\Ptransmission$ and model $\EnergyTrack$ in the absence of
$\Ptransmission$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the
modification of $\Sigma^{(d)}_j$ that accounts for occlusion.  The results show that
use of continuous occlusion model improves the localization accuracy in terms
of all three metrics: translation, yaw and dimension error.

>>>>

\subsection{Localization Experiments}
We report error in three metrics translation error (t) in meters per car, yaw
error (yaw) in radians per car and dimension error is again meters per car. The
results are shown in Table~\ref{tab:localizationExperiment}.  We compare four
combinations of energies as shown in the table.  The energy $\EnergyTrackNoOcc$
represents the point tracks energy modeled with accounting for occlusion, i.e.,
we remove the term $\Ptransmission$ and model $\EnergyTrack$ in the absence of
$\Ptransmission$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the
modification of $\Sigma^{(d)}_j$ that accounts for occlusion.  The results show that
use of continuous occlusion model improves the localization accuracy in terms
of all three metrics: translation, yaw and dimension error.
